Fitting the Undetected: Light-curve Feature Estimation in the Presence of Non-detections

### 2012-07-05 tex/ms.tex
ms updated and TODO list added

@@

>>>>

Figure \ref{fig:miraP} shows the estimated periods for standard Lomb-Scargle against the periods from our censored Fourier model for 2538 likely Mira variables chosen from the MACC catalog (these were chosen such that $P$(Mira) $>0.5$.)  For 12.6\% of these objects, the censored period is twice that of the Lomb-Scargle period, while for 0.51\% it is triple (show examples).  This occurs because of XYZ.  For 85.5\% of all objects, the periods are consistent to $\pm$5\%.

\begin{figure*}
\begin{center}
\includegraphics[angle=0,width=6.5in]{../plots/mira_periods_LS_vs_Censored.pdf}
\end{center}
\caption{ .  \label{fig:miraP}}
\end{figure*}

Figure \ref{fig:miraPA} shows the period-amplitude relationship for the set of Mira variables, with periods and amplitudes estimated by standard Lomb-Scargle (left) and the censored model (right).  Results show that XYZ.

\begin{figure*}
\begin{center}
\includegraphics[angle=0,width=6.5in]{../plots/mira_period_amplitude_relation.pdf}
\end{center}
\caption{ .  \label{fig:miraPA}}
\end{figure*}

@@

As a selection criterion (simulated data?)
